\documentclass[11pt]{report}
\begin{document}
\title{Autism Simulator}
\author{Ashley Peacock}
\maketitle
\tableofcontents
\chapter{Introduction}

\section{Selecting a project}


\chapter{Literature review}
\section{What is Autism?}
Autism is a spectrum disorder that affects social communication, social imagination and social interaction. The range and severity of difficulties will vary for each individual. For example those with Asperger's syndrome may have more problems with socialising whereas those with Low-functioning autism may only speak single words or short sentences. Aspergers is therefore looked upon as a 'hidden condition', making it even harder for the general public to understand. 
In addition to these issues, often those with autism experience Sensory Processing Disorder. 
\subsection{Triad of Impairments}
\subsubsection{Sensory overloads}
\subsubsection{Meltdowns}
\subsubsection{Fears}
\subsection{Impact and Prevalence}
Impact these difficulties have on a day to day life.
How many people in the world have autism or are affected by it.

The impact on the life of someone with Autism can vary. 

\subsection{Public perception}
What the public currently think of autism.
\subsubsection{Impact in school}
\subsubsection{Problems with training}

\chapter{Design process}
\section{Interviews}

\section{Game design}
\subsection{House design}
House design choices. 
\subsection{Character}
\subsubsection{Autism aspects to convey}
\subsection{Design of sensory system}
\subsection{Story boards}

\chapter{Prototype}

\section{Implementation}
What was in the prototype.
\section{Evaluation}
\subsection{Expert feedback}
\subsection{User feedback}
\section{Improvements}

\chapter{First version}

\end{document}