
\chapter{Formative evaluation: First version}
The formative evaluation primarily focused on user experience and game play with an further goal of making sure the simulation was successful in teaching awareness of at least one attribute of autism. 

Three key goals were identified for the formative evaluation: 
\begin{enumerate}
\item Check that the game play controls were intuitive with no obvious problems. 
\item Ensure that users can complete the first mission without getting bored or too frustrated. 
\item See if the user could learn at least one new thing about autism that they did not previously know: ideally they would learn about or become aware of sensory problems.
\end{enumerate}

Additional goals expected to be satisfied through iteration:
\begin{enumerate}
\item Identify areas where a user may need help or prompts;
\item Obtain qualitative information on how the user was interacting and playing the game, rather than their thoughts on the project;
\item Improve the user’s ability to understand the simulator and environment with minimal materials and instructions such that future users would be able to simply "pick up and play".
\end{enumerate}

Participants were recruited from friends of the researcher: although most were aware of the project, none had played with or previously seen it. The following table gives background information on participants involved in the evaluation and represents the order in which they participated.

\begin{table}[H]
    \begin{tabular}{| p{2cm} | p{9cm} | p{3cm} | p{3cm} |}
    \hline
    Name & Background information & O=Online. P = in person & Location \\
    \hline
    \hline
    P1 & Final year chemistry student. Minimal game experience & P & My home\\ \hline
    P2 & Graduated with a degree in Philosophy and Economics. Minimal gaming experience & P & Own home \\ \hline
    P3 & Final year Masters of Informatics student. Designing an app for visually impaired. Studied HCI & P & Own home \\ \hline
    P4 & 4th year Social sciences. Medium game experience & P & Own home \\ \hline
    P5 & Final year Computer science. Studied HCI and was taking Adaptive Learning Environments course and had taken the graphics course. Large game experience & P & My home \\ \hline
    P6 & Final year Computer science and has ADHD. Spent a year abroad working in graphics. Took courses in HCI. Large game experience & P & My home \\ \hline
    P7 & Final year chemistry student & O & -\\ \hline
    P8 & Final year chemistry student & O & - \\ \hline
    \end{tabular}
    \caption{Test}
\end{table}

The participants come from a variety of backgrounds and courses and were felt to be able to give an all round picture of user expectations. The three participants from a computer science background, having taken courses in Graphics and HCI, would be more aware of the theoretical pitfalls in interaction and interface design, thinking not only from their own perspective but from that of other users, and thus be in a good position to offer criticisms and suggestions for solving these problems.

\section{Methods}

Evaluation sessions took approximately 30-45 minutes each, depending on the game experience of the user, including questions before and after. Only qualitative information from participants was extracted, owing to the small sample. All evaluations took place at either the home of the researcher or the participant. The process was iterative and the system was improved based on feedback, where time constraints between evaluations permitted.

Participants were asked about their prior experience with computer games, in addition to prior knowledge of autism. The first six participants participated in person. The first four participants were verbally asked about their previous knowledge, which was noted. This was found to be inefficient with some information being lost; the later four participants completed a questionnaire with the same questions, both before and after using the simulator. The final two participant sessions were conducted solely on-line; they were sent the questionnaires with instructions and a link to download it. 

Formative pre-interaction questions:
\begin{enumerate}
\item What can you tell me about Autism and their difficulties?
\item What is your current skill with computer games?
\end{enumerate}

After questionnaire 
\begin{enumerate}
\item What can you tell me about autism and their difficulties?
\item Did you find the game controls intuitive?
\item Please include any additional feedback or suggestions such as parts you may have found difficult or what you feel could be improved.
\end{enumerate}

No materials were provided and participants were only told ``This is an autism simulator’’. One of the goals is to ensure that the simulator can be played without needing to read instructions and sit through tutorials. This is due to awareness that some individuals will often skip instruction manuals and opt to learn first by experience, later seeking help or consulting guides if they run into difficulty and cannot solve problems on their own.

Participants were directed and encouraged to verbalise their thinking process whilst being observed and given directions such as ``Go to the kitchen’’ or ``Go to the bathroom and click on the tooth brush’’. This is expected to change at a later stage, where fewer directions would be required, and only given on request. If directions were not requested by the user, but there was evidence of difficulty, the user would be asked ``I see you trying to open the door but it is not working. Can you explain how you are trying to do that’’. Prompts and directions given were recorded on pen-paper for two reasons 1. They could provide an indication of in-game prompts required for users and 2. Noting difficulties may shed light on alternative ways of doing things, or be an indication of general game-play problems if they arose for other users.

\section{Results}
The system was iterated upon after participant 1, participants 2, 3-4(inclusive), participants 5-6 and again after 7 and 8.

\subsection*{Participant 1}

For the first evaluation session the participant was just asked to play the ``Mission mode’’. However, in-spite of information and instructions at the beginning which were displayed as a description box, the participant found it extremely difficult and explicit instructions needed to be given. Further problems were quickly identified with entering and leaving rooms; the door model was split into both ``handle’’ and ``door’’ and the user was clicking the handle, rather than the door itself, which is the norm for most first person games. They were invited to play the explore mode first in order to become familiar with the environment but they still encountered some problems with moving around and quickly experienced meltdowns, with some confusion. Once it was indicated that there was a tool-tip, explaining actions available when you mouse over objects in the scene, this process became easier. 

For all later formative evaluation sessions, participants were asked to play the ``Explore mode’’, followed by the ``Mission mode’’. The latter encompassed just the morning routine, as this part was most tested and ready and could be conducted within the evaluation timeframe. This choice indicated an improvement and participants were less confused and were able to all complete the missions. Participants were given additional information that they were to ``play an Autism simulator. Use the explore mode and then the mission mode’’.

Finally a key problem was identified: when descriptions and alerts popped up contentment could still reduce, so whilst the user was reading information a meltdown could occur, making it further difficult to learn about the environment itself.

Suggested improvements:
\begin{enumerate}
\item Change the door model so handle and door are no longer separated spatially. 
\item When hovering over the door with the cross-hair, make the tool-tip change to indicate what room they will be moving into. 
\item Provide additional messages explaining causes of meltdowns.
\item Game automatically pauses when description boxes are up.
\end{enumerate}

\subsection*{Participant 2} 
Participant 2 was able to comment on some features of autism. Throughout the process they were frequently experiencing sensory overloads and meltdowns and were given prompts on how to avoid these.

Prompts/questions:
\begin{enumerate}
\item To watch the contentment;
\item Interact with dinosaur;
\item Watch the tool tip to see available actions;
\item Needed reminder what the morning routine was;
\item Unsure of causes of meltdowns at times.
\end{enumerate}

Suggested improvements:
\begin{enumerate}
\item Move contentment bar to the middle of the screen and make it larger or more obvious. 
\item Put morning routine on the wall for user to look at/observe. 
\item Provide additional messages on cause of meltdowns or sensory overloads. Messages will change giving a new piece of information each time.
\item Morning routine timer does not start until after the description box has been pressed. 
\end{enumerate}

Meltdowns were happening far too quickly to give the user time to think about the cause, although comments were made that they were really attempting to in an attempt to ``prevent that horrible noise’’. The participant commented that they felt the game play controls were intuitive, in spite of not often having played first-person computer games. 

All suggested improvements were implemented. The rate in which contentment drops was reduced by 20\%.

\subsection*{Participant 3 and 4}
P4 went through the simulator extremely quickly and is still to date the only participant to have completed the morning routine without a single meltdown, although they did comment that this was occurring too quickly. No prompts were required apart from a reminder to look at the mill in the living room. 


Prompts/questions/comments(P3):
\begin{enumerate}
\item Asking what was causing sensory overloads in specific situations (e.g. the living room where there is a light extremely high up that is not obvious).
\item Was not clear that they could interact with the dinosaur.
\item Was not clear when mission was completed, with the next ``Afternoon’’ routine starting straight away.
\item Where is that radio sound coming from?
\item Pointed out that top right were the objectives for the morning routine.
\end{enumerate}

Suggested improvements:
\begin{enumerate}
\item Fix the problem in relation to light objects not on the screen causing overloads.
\item Big, pretty ``Mission complete’’ after each mission, with a delay before the next one starts.
\item Reduce the speed at which contentment drops.
\item Increase the size of tool tip as the issue of the user not being aware of the bedroom object interaction has arisen a few times, and this should be the room in which users should have the most ease. 
\item Adding a drop shadow to thoughts might make them easier to improve.
\item Change meltdown sound from a radio to tv static. 
\item Add text ``Objectives’’ about images for morning routine. 
\end{enumerate}

The first of these was implemented after consultation with someone who had Autism and severe sensory difficulties.

The drop shadow could not be added without some difficulty, so was left for a later improvement. Contentment was still seen to be occurring too quickly and the threshold was reduced by a further 30\%. 

Finally, it was decided that one additional improvement should be made that was not commented on: the addition of a fluorescent light. As contentment was no longer dropping as quickly, and with the removal of sensory ``light’’ objects not being a problem if they were not on screen, more ``hazardous’’ objects needed to be added that would be problematic even when they were not on screen, in order to maintain difficulty. A fluorescent light was selected as these are a highly prevalent difficulty for people with autism. 

\subsection*{Participant 5 and 6}

Participant 6, whom has ADHD, offered a good opportunity to test 3 of ``additional goals’’ as they did not read any of the description boxes or information. In spite of this, very few questions were asked, and most difficulties encountered were quickly solved without a need for prompts. P6 was extremely vocal, indicating their understanding of the simulation throughout.

Prompts/questions/comments(P6):
\begin{enumerate}
\item Prompted to move closer to objects when initially could not click (thoughts of ``I can’t reach that wasn't seen’’)
\item Why don't I like cheese in the kitchen but I like grapes?
\item Prompt to check the routine on the wall.
\end{enumerate}

Prompts/questions/comments(P7):
\begin{enumerate}
\item Why is the tooth brush causing a problem?
\item Didn't notice the mill in the living room could be interacted with which could increase contentment and lessen sensory problems
\item Thoughts still not clear however the JMonkey app statistics were in view which made it difficult to see thoughts.
\item Why is the light flicking in the kitchen?
\item Difficulty clicking on the toothbrush in the bathroom and had to be prompted that it was possible to click.
\end{enumerate}

Suggested improvements:
\begin{enumerate}
\item Information on the tooth brush causing tactile sensory issues. 
\item Add a thought for the mill in the living room to hopefully make it more obvious that this can be interacted with. 
\item Description box in explore mode for when the user first goes into the kitchen explaining about Fluorescent lights. 
\item Adjust so that the user does not have to directly click on object with cross hair.
\item Sizes of thoughts increased in an attempt to combat this without the use a text shadow. 
\end{enumerate}

Option 4 was not implemented and left for a later improvement as it was uncertain how to do this with ease. 

\subsection*{Participant 7 and 8}
Due to the evaluation not being conducted in person, feedback was based purely on answers to the questionnaire and a few general questions afterwards. 

Comments from questionnaires (both participants):
\begin{enumerate}
\item Had not noticed mill in living room although commented ``I just wanted to get out of there because of the hoover!’’
\item Had issues with controls and trying to click instead of pressing space bar.
\item Trouble clicking toothbrush.
\item Visual effects making it difficult to find stimming objects.
\end{enumerate}

As the last option is thought to be desirable this will not be a suggested improvement. 

Suggested improvements:
\begin{enumerate}
\item Increase size of tool tip/make it more obvious.
\item Have thoughts as ``Boxes’’ at the bottom.
\end{enumerate}

\subsection*{Results summary}
Results for goals 1-3:

\begin{table}[H]
\begin{tabular}{|p{1cm} | p{2cm} | p{3cm} | p{3cm} | p{2cm} | p{4cm}|}
\hline
Participant & Controls & Prior autism knowledge & Later autism knowledge & Complete & Comments \\
\hline
\hline
    P1 & Y & Social difficulties & Meltdowns & N & Controls intuitive but difficulty interacting with environment \\ \hline
    P2 & Y & Social difficulties & Sensory overloads caused by light and sounds. Meltdowns result in a loss of control & Y & Found myself thinking about the ways to approach the situations and what I could do to prevent that horrible noise \\ \hline
    P3 & Y & Social difficulties. Special interests & Sensory difficulties. Routine & Y & Thoughts hard to see, add a drop shadow. \\ \hline
    P4 & Y & Social difficulties & Sensory overloads. Meltdowns. & Y &  \\ \hline
    P5 & Y & Makes it hard to feel empathy thus hard to understand others feelings and needs &  & Y & Add ability to interact with small objects such as toothbrush without having to aim cross hair exactly at is.  \\ \hline
    P6 & Y  & Difficulty with social skills. Special interests in maths and a good memory & Routine. Uncomfortable around people, loud noises, bright lights & Y   & Reminder about routine helpful \\ \hline
    P7 & N  & Affects ability to focus for long periods of time. Social difficulties. People might act in a way that causes them to feel anxious. & Sensor overloads caused by visual, auditory or tactile. String routine required and must not be deviated from & Y  & Wanted to use direction keys to move instead of `W' key \\ \hline
    P8 & Y & Aspergers is a form of autism & Visual disturbances due to sensory overloads. Affects emotional response of a person. & Y & Trouble brushing teeth. Visual effect can scupper changes of finding stimming since it is difficult to see what is going on around you \\
     \hline    
\end{tabular}
\end{table}

Full responses from participants 4-8 are included in the appendix. 

\section{Conclusions}
As is consistent with previous research on public knowledge of Autism, no participant commented on the related sensory issues, although this is a very small sample. Most commented on social issues, or that they knew of the existence of autism and the isolation felt. An indication of improved knowledge in each participant is seen, as a result of playing the simulator, and thus the first goal was achieved. 

Improvements to the process would have been to have verbally recorded the responses and comments made all participants, so unfortunately it is felt that some information was lost, which may be responsible for some of these issues re-appearing in the summative evaluation. By using the on-line questionnaire, information acquired was much more detailed in relation to the goals and feedback was better documented. The responses of most participants after playing the simulator were related to sensory problems and no-one particularly commented on information in the description boxes. From this it might be inferred that direct experience is shown to be a better teacher than conveying knowledge in the description boxes even though it was in an virtual, and hopefully fun, environment. Thus a good later addition would be to add more ``experience’’ scenarios, such as contending with weather changes or literal language interpretation.  

Game controls were generally found to be intuitive in spite of having some novice game players. One participant commented on using direction buttons instead but the decision was made not to change this as many games use the same game controls as used here, and the preference of one participant was not enough to warrant a change. If similar problems are found later for other users, this will be re-considered. 

In-spite of a change in methodology and asking users to play the explore mode with in-game hints offered, participants still found the task of completing the morning routine difficult. It was found that the environment was too harsh and participants were finding it difficult to get become accustomed to controls, to think about what was happening and why, and to develop avoidance strategies; effectively, there was too great a cognitive load to be able to direct attention to simply learning and exploring. Contentment was reducing too quickly and meltdowns were occurring too often, and sometimes the cause could not be identified. The latter confusion regarding the cause was improved, although consultation was required as interviews indicated that overloads occurred sometimes without knowing why and it took experience to learn this. This was solved by heightening the effects of lights when the user looked at them, rather than just being near them.

However, it is felt that a degree of difficulty is required, in order to give an incentive for people to find new strategies for overcoming problems, and to facilitate thinking from the perspective of someone with autism, i.e ``Ok, I am faced with these difficulties, but how do I solve them?’’. It is hoped that the need to problem solve and to find new strategies could further aid teaching, as long as there was the understanding that any strategies derived should not be enforced. 

With each iteration of the system, it was observed that the types of questions from participants were changing and different problems came to light. Instead of asking questions related to ``What do I do here?’’, participants were asking questions such as ``What's the problem the person with autism has with cheese?’’, ``Why does the tooth brush hurt?’’. The transition in form and focus of questions suggests that the game-play greatly improved, although more formative evaluation would need to be conducted to see if this is indeed the case. Owing to time constraints, minimal further improvements were implemented before the summative evaluation. 

It has become clear that not all details and aspects can be necessarily given to users: there were small details such as the mill that some picked up on and others did not. One suggestion was to improve the ``Explore mode’’ with an additional tutorial mode, potentially with a list of simple tasks that will be ticked off when complete. This is left as potential future work.

